**Results Template**

### 2021-09-28 1_descriptive.Rmd
dt rt

```{r}
ggplot(df, aes(yoni_total)) + geom_histogram()
ggplot(df, aes(BES_total)) + geom_histogram()
ggplot(df, aes(yoni_total, BES_total)) + geom_point()
ggplot(df, aes(HCT_accuracy)) + geom_histogram()
ggplot(df, aes(MAIA_total)) + geom_histogram()
ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
```

>>>>

```{r independent var}
ggplot(df, aes(yoni_total)) + geom_histogram()
ggplot(df, aes(BES_total)) + geom_histogram()
ggplot(df, aes(yoni_total, BES_total)) + geom_point()
ggplot(df, aes(HCT_accuracy)) + geom_histogram()
ggplot(df, aes(MAIA_total)) + geom_histogram()
ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
```

```{r dependent var}
ggplot(df, aes(instruction, DT_RT)) + geom_boxplot()
ggplot(df, aes(instruction, DT_confidence)) + geom_boxplot()
ggplot(df, aes(condition, DT_RT)) + geom_boxplot()
ggplot(df, aes(condition, DT_confidence)) + geom_boxplot()
```

```{r}
df %>% 
  group_by(ID, condition, instruction) %>% 
  summarise(confidence = mean(DT_confidence, na.rm = TRUE),
            yoni_total = mean(yoni_total, na.rm = TRUE)) %>% #create a new df for plot
  ggplot(aes(x = yoni_total, y = confidence, colour = instruction)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~condition)
```

### 2021-09-28 2_inferential.Rmd
dt rt

```{r}
model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
report(model)
parameters(model, effects = "fixed")
interactions::cat_plot(model, pred = instruction, modx = condition)
#R2 does not account for random effects
#interaction is significant
```

>>>>

```{r}
model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item), df)
report(model)
parameters(model, effects = "fixed")
interactions::cat_plot(model, pred = instruction, modx = condition)
means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
means
contrasts <- modelbased::estimate_contrasts(model, contrast = c("condition", "instruction"))
ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
  geom_line(aes(group = condition)) +
  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
#R2 does not account for random effects
#interaction is significant
performance::performance(model)
```

### 2021-09-28 index.Rmd
dt rt

```{r warning=FALSE, message=TRUE, results='asis'}
library(bayestestR)
library(parameters)
library(performance)
library(report)
library(see)
library(ggplot2)

>>>>

```{r warning=FALSE, message=TRUE, results='asis'}
library(bayestestR)
library(parameters)
library(performance)
library(report)
library(see)
library(tidyverse)
library(lme4)
library(modelbased)

### 2021-09-28 scripts/claudia/data processing.Rmd
dt rt

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)] %>% 
    mutate(trial = c(1:80)) %>% 
    mutate(condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

@@

data <- mydata %>% 
  rename(item = V1,
       style = V2,
       instruction = V3,
       question = V4,
       DT_confidence = V35,
       DT_confidenceRT = V36,
       ID = V47) %>%

  mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
  mutate(DT_confidenceRT = as.numeric(DT_confidenceRT)) %>% 
  mutate(instruction = as.factor(instruction)) %>% 
  mutate(ID = as.numeric(ID)) %>% 
  left_join(inclusion) %>%

  select(ID, trial, condition, inclusion, inclusion2, everything()) #move columns to front

results <- data %>% 
  group_by(ID, instruction, style) %>% 
  summarise(DT_confidence_avg = mean(DT_confidence), DT_confidenceRT_avg = mean(DT_confidenceRT))

@@

```{r combine data}
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  left_join(read.csv("deceptiontask_processed.csv")) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))

>>>>

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
    mutate(trial = c(1:80)) %>% 
    mutate(condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

@@

data <- mydata %>% 
  rename(item = V1,
       style = V2,
       instruction = V3,
       question = V4,
       social_start = V29,
       social_stop = V31,
       DT_confidence = V35,
       DT_confidenceRT = V36,
       polyg_start = V43,
       polyg_stop = V45,
       ID = V47) %>%

  mutate(DT_confidence = as.numeric(DT_confidence)) %>% 
  mutate(instruction = as.factor(instruction)) %>% 
  mutate(social_start = as.numeric(social_start)) %>% 
  mutate(social_stop = as.numeric(social_stop)) %>% 
  mutate(polyg_start = as.numeric(polyg_start)) %>% 
  mutate(polyg_stop = as.numeric(polyg_stop)) %>% 
  mutate(ID = as.numeric(ID)) %>%
  mutate(DT_RT = ifelse(condition == "Social", social_stop - social_start,
         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%

  left_join(inclusion) %>%
  select(ID, trial, condition, inclusion, inclusion2, everything()) #move columns to front

results <- data %>%
  group_by(ID, instruction, style) %>%
  summarise(DT_RT_avg = mean(DT_RT, na.rm = TRUE),
            DT_confidence_avg = mean(DT_confidence, na.rm = TRUE))

@@

```{r combine data}
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  select(-c(contains("start")|contains("stop"))) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))
